The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Add stashed changes

## Read metadata for all theses
all_theses <- read_xlsx(path = here(data_path, "theses-all.xlsx"))

@@

pdf_paths <- here(data_path, emu$file_name)
```

@@

>>>>

# TODO replace the following lines with the metadata included in the package
# emu_metadata <- data(emu_metadata)
## Read metadata for all theses
all_theses <- read_xlsx(path = here(data_path, "theses-all.xlsx"))

@@

# TODO replace this and next code chunk with reading `text_raw` from the package
# emu <- data(emu_raw)
pdf_paths <- here(data_path, emu$file_name)
```

@@

# TODO Explore including concatenated collocations in the topic model
